Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-08 analysis/paper/paper.Rmd
Minor edits

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the least cost.

>>>>

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional licence, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.
